\section{Bibliographies}

For adding a bibliography to your document we recommend using biblatex\footnote{an alternative is bibtex}.
All references you want to cite should be added to one (or more) .bib files.
Each entry in your bibfile contains all the information latex needs to format the citation and bibliography entry.
Once again, style is separated from content here and you can choose your citation style in the preamble of the document.
\begin{figure}[h!]
    \begin{verbatim}
    \usepackage{biblatex}[backend=biber, style=apa, citestyle=apa]
    \addbibresource{biblatex-examples.bib}
    \end{verbatim}
    \caption{setting up a bibliography}
    \label{fig:bibliography}
\end{figure}

In the figure above (\ref{fig:bibliography}) the first line imports biblatex and sets the citation style to apa\footnote{more citation styles here: \url{https://www.overleaf.com/learn/latex/Biblatex_citation_styles}}.
The second line adds a bib file with example citations (use your own here).

Entries from your bibfile are cited using \textit{\textbackslash cite\{referencelabel\}}. Each entry in your bib file(s) has a label that can be used with cite to automatically place a citation at the spot where you use the command and add the entry to your bibliography if it is not yet added.

You can also add items to your bibliography without citing them in the text by using \textit{\textbackslash nocite\{reflabel\}}.

For example: (\cite{springer} \cite{aristotle:anima})

\nocite{companion}
\nocite{iliad}

While you could write these entries yourself, we recommend using a reference manager such as Zotero to create them automatically.\footnote{Bonus tip: Zotero offers an extension for Chrome/Firefox that extracts citations from websites,journals or online pdfs automatically}. Zotero offers exporting your collections to .bib files and can keep them updated automatically if you add new entries\footnote{Bonus tip: consider installing "better bibtex" should you choose to use Zotero \url{https://retorque.re/zotero-better-bibtex/}}.

Finally, add \textit{\textbackslash printbibliography} where you want your bibliography. It will be formatted in the format you chose when importing biblatex.